Locality and Computational Reliability of Linear Response Calculations for Molecular Systems

### 2019-01-23 Supplementary_material.tex
update plot and supplementary
update

The growth of the localized sector with the number of atoms of the molecule seems to be a general feature. It can simply explained by observing that bigger molecules behave as wider potential wells and possess a high number of localized Kohn-Sham (KS) orbitals that span a wide energy range. In a simplified two-levels picture, in which $\op V'=0$, the KS empty orbitals $\psi_a$ coincide with the excitation modes defined in eq. (17) and the associated energy is parametrized as $\Omega_a=\epsilon_a-\epsilon_p$. In this case to the increase of the energy range spanned by the localized orbitals it directly corresponds a richer sector of localized excitations.
When $\op V'$ is switched on the excitation modes are expressed as a combination of KS orbitals but the presence of a high number of localized orbitals allows for a rich sector of localized excitations, as confirmed by the results of Fig. \ref{exc-land}.

\begin{figure}[h]
    \centering
    \begin{subfigure}[t]{0.48\textwidth}
        \centering
        \includegraphics[width=\linewidth]{C60_ExcitationLandscape.eps} 
        \caption{$C_{60}$} \label{fig:b}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.48\textwidth}
        \centering
        \includegraphics[width=\linewidth]{Aflatoxin_ExcitationLandscape.eps} 
        \caption{Aflatoxin} \label{fig:a}
    \end{subfigure}
    \caption{Excitation landscape for the $C_{60}$ (panel a) and the Aflatoxin (panel b) molecules computed accordingly to the procedure described  in the appendix C. Black circles represent the localized sector and blue squares describe the pseudo-continuum one. }
\label{exc-land}
\end{figure}

>>>>

The growth of the localized sector with the number of atoms of the molecule seems to be a general feature. It can simply explained by observing that bigger molecules behave as wider potential wells and possess a high number of localized Kohn-Sham (KS) orbitals that span a wide energy range. 
A numerical evidence in support of this argument is presented in Fig. \ref{dos}, where the DOS of the KS (bound) orbitals of the Aflatoxin and $CO$ molecules are directly compared.  
In a simplified two-levels picture, in which $\op V'=0$, the KS empty orbitals $\psi_a$ coincide with the excitation modes defined in eq. (17) and the associated energy is parametrized as $\Omega_a=\epsilon_a-\epsilon_p$. In this case to the increase of the energy range spanned by the localized orbitals it directly corresponds a richer sector of localized excitations.
When $\op V'$ is switched on the excitation modes are expressed as a combination of KS orbitals but the presence of a high number of localized orbitals allows for a rich sector of localized excitations, as confirmed by the results of Fig. \ref{exc-land}.

\begin{figure}[h]
    \centering
    \begin{subfigure}[t]{0.48\textwidth}
        \centering
        \includegraphics[width=\linewidth]{C60_ExcitationLandscape.eps} 
        \caption{$C_{60}$} \label{fig:b}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.48\textwidth}
        \centering
        \includegraphics[width=\linewidth]{Aflatoxin_ExcitationLandscape.eps} 
        \caption{Aflatoxin} \label{fig:a}
    \end{subfigure}
    \caption{Excitation landscape for the $C_{60}$ (panel a) and the Aflatoxin (panel b) molecules computed accordingly to the procedure described  in the appendix C. Black circles represent the localized sector and blue squares describe the pseudo-continuum one.}
\label{exc-land}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=9cm]{DOS_Afla&CO.eps} 
    \caption{DOS of the (bound) KS states for the Aflatoxin and the $CO$ molecules. }
\label{dos}
\end{figure}
